Reassessing the Impact of Dynamic Slicing in SFL

### 2019-01-25 paper/ijcai/paper.tex
results for time and mockito added

        \lang{}            &  & \\ 	
        \cmath{}           &  & \\
        \closure{}          &  & \\	
		\chart{}			& 59.30\% & 53.64\% \\ 	
        \jtime{}            &  & \\	
        \mockito{}          &  & \\

@@

\subsubsection{RQ1: \textit{Diagnosis capability}}

		            & \% top-5 & \% top-10  & $\Delta$ & \# top-5 & \% top-5 & \# top-10 & \% top-10 &  \\ 
		\midrule
		% \lang{}            & 84.60 \% & 84.60 \% & 0 \%       \\   %\commentst{& 124   &  -}\\
		% \cmath{}           & 82.08 \%  & 85.85 \% & 3.77 \%     \\   %\comments{& 177   &  -}\\
		% \closure{}         & 62.41 \%  & 72.18 \%  & 9.77 \%     \\   %\comments{& 350   &  -}\\
		\chart{}           & 84.6\%  & 92.3\% & 7.7\%  & 20 & 76.9\% & 22 & 84.62\% & 26    \\  %\comments{& 92    &  -}\\
		% \jtime{}           & 77.78 \%  & 100.00 \% & 22.22 \%       \\   %\comments{& 76    &  -}\\
		% \mockito{}         & 63.16 \%  & 71.05 \% & 7.89 \%    \\     %\comments{& 118   &  -}\\
		\bottomrule
	\end{tabular}
  \caption {Diagnosis capability if only considering the \sfl{} results for each version (no slicing applied)}
  \label{table:fsws}
\end{table*}

\subsubsection{RQ2: \textit{How often DS misses faulty statements?}}

In \textbf{RQ2}, we evaluate how often DS misses faulty statements, since it is one of the main problems of dynamic slicing techniques.

@@

@@

\subsubsection{RQ3: \textit{How effective is the \comb{} combination for bug localization?}}

In \textbf{RQ3}, we intend to evaluate the impact of combining \ds{} to improve \ds{}.

@@

		\bottomrule
	\end{tabular}
	\caption {\Sof{This can be a barchart} Diagnosis Performance for using \comb{}-5 and \comb{}-10 instead of \sfl{}}
	\label{tab:diagnosis}
\end{table}
\normalsize

\begin{table*}[h]
	\centering
	\begin{tabular}{@{}llll@{}}
\toprule
  & SFL                    & \comb{}-5                 & \comb{}-10                 \\ \midrule
Mean & 531.04     & 745.71   & 715.62    \\ \midrule
Median & 17.5                   & 15.25                & 15.25                 \\ \midrule
Variance & 1520.09      & 1794.86   & 1803.11    \\ \midrule
Shapiro-Wilk & \makecell{W = 0.40 \\ p-value = 2.95 x $10^{-9}$} & \makecell{W = 0.48 \\ p-value = 1.54 x $10^{-8}$} & \makecell{W = 0.46 \\ p-value = 9.11 x $10^{-9}$}  \\ \midrule
Friedman & \multicolumn{3}{c}{\makecell{$\chi^{2}$ = 10.46 \\ p-value = 2.95 x $10^{-9}$}} \\ 
\bottomrule
\end{tabular}
  \caption {Statistical tests \Sof{Only for \chart{} yet}}
  \label{table:st}
\end{table*}

\begin{figure}[h]
		\includegraphics[width=0.45\textwidth]{figures/heatmap_nemenyi_result.pdf}
		\caption{Nemenyi post-hoc analysis results \Sof{Only for \chart{} yet}}
		\label{fig:performance}
\end{figure}

@@

@@

	\begin{figure*}
		\centering
		\includegraphics[width=\textwidth]{figures/Chart_abs.pdf}
		\caption{Comparing the rank of all faulty statetments for each project version obtained by \sfl{} and \comb{} considering the top-5 and top-10 of classes}
		\begin{tabular}{r@{: }l}
			SFL & Rank of all faulty statements only using \sfl{}\\
			LS-$5$& Rank of all faulty statements after slicing the top-5 classes \\
			LS-$10$& Rank of all faulty statements after slicing the top-10 classes 
		\end{tabular}
		\label{fig:ranking}
	\end{figure*}

	\begin{figure*}
		\centering
		\includegraphics[width=\textwidth]{figures/Chart_abs_imp.pdf}
		\caption{\sfl{} rank improvement by applying \ds{} to the top-5 and top-10 classes of each project version}
		\begin{tabular}{r@{: }l}
			IMP-$5$& \sfl{} rank improvement by applying \ds{} to the top-5 classes \\
			IMP-$10$& \sfl{} rank improvement by applying \ds{} to the top-10 classes
		\end{tabular}
		\label{fig:performance}
	\end{figure*}

>>>>

        \lang{}            &  & \\ 	
        \cmath{}           &  & \\
        \closure{}          &  & \\	
		\chart{}			& 59.30\% & 53.64\% \\ 	
        \jtime{}            & 17.27\% & 32.92\%\\	
        \mockito{}          & 16.99\% & 21.67\%\\

@@

\subsubsection{RQ1: \textit{How often DS misses faulty statements?}}

In \textbf{RQ1}, we evaluate how often DS misses faulty statements, since it is one of the main problems of dynamic slicing techniques.

@@

		            & \% top-5 & \% top-10  & $\Delta$ & \# top-5 & \% top-5 & \# top-10 & \% top-10 &  \\ 
		\midrule
		% \lang{}            & 84.60 \% & 84.60 \% & 0 \%       \\   %\commentst{& 124   &  -}\\
		% \cmath{}           & 82.08 \%  & 85.85 \% & 3.77 \%     \\   %\comments{& 177   &  -}\\
		% \closure{}         & 62.41 \%  & 72.18 \%  & 9.77 \%     \\   %\comments{& 350   &  -}\\
		\chart{}           & 84.6\%  & 92.3\% & 7.7\%  & 20 & 76.9\% & 22 & 84.62\% & 26    \\  %\comments{& 92    &  -}\\
		\jtime{}           & 77.78 \%  & 100.00 \% & 22.22 \%  & 22 & 81.48\% & 23 & 85.19\% & 27     \\   %\comments{& 76    &  -}\\
		 \mockito{}         & 63.2\%  & 71.1\% & 7.9\%   & 27 & 71.05\% & 30 & 78.95\% & 38 \\     %\comments{& 118   &  -}\\
		\bottomrule
	\end{tabular}
  \caption {Diagnosis capability if only considering the \sfl{} results for each version (no slicing applied)}
  \label{table:fsws}
\end{table*}

@@

\subsubsection{RQ2: \textit{How effective is the \comb{} combination for bug localization?}}

In \textbf{RQ2}, we intend to evaluate the impact of combining \ds{} to improve \ds{}.

@@

\begin{table}[h]
	\centering
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{ccc}
		\toprule
		$\Delta$$C$             &  \comb{}-5  & \comb{}-10 \\ 
		\midrule
		$<0$  & 31.87\% & 25.27\% \\ 
		$=0$  & 26.37\% & 26.37\% \\ 
		$>0$  & 41.76\% & 41.76\% \\

		\bottomrule
	\end{tabular}
	\caption {Diagnosis Performance for using \comb{}-5 and \comb{}-10 instead of \sfl{} \Sof{Considering \chart{}, \jtime{}, \mockito{}}}
	\label{tab:diagnosis}
\end{table}
\normalsize

\begin{table*}[h]
	\centering
	\begin{tabular}{@{}llll@{}}
\toprule
  & SFL                    & \comb{}-5                 & \comb{}-10                 \\ \midrule
Mean & 521.59     & 855.34   & 758.06    \\ \midrule
Median & 57.21      & 260.33                & 109                \\ \midrule
Variance & 1021.65      & 1307.70   & 1275.34    \\ \midrule
Shapiro-Wilk & \makecell{W = 0.56 \\ p-value = 4.00 x $10^{-15}$} & \makecell{W = 0.69 \\ p-value = 1.81 x $10^{-12}$} & \makecell{W = 0.65 \\ p-value = 1.68 x $10^{-13}$}  \\ \midrule
Friedman & \multicolumn{3}{c}{\makecell{$\chi^{2}$ = 7.22 \\ p-value = 0.027}} \\ 
\bottomrule
\end{tabular}
  \caption {Statistical tests \Sof{Considering \chart{}, \jtime{}, \mockito{}}}
  \label{table:st}
\end{table*}

\begin{figure}[h]
		\includegraphics[width=0.45\textwidth]{figures/heatmap_nemenyi_result.pdf}
		\caption{Nemenyi post-hoc analysis results \Sof{Considering \chart{}, \jtime{}, \mockito{}}}
		\label{fig:performance}
\end{figure}

@@

			\bottomrule
		\end{tabular}
		\caption {\chart{} - Diagnosis Performance for using \comb{}-5 and \comb{}-10 instead of \sfl{}}
		\label{tab:diagnosis}
	\end{table}
	\normalsize

	\begin{table}[h]
		\centering
		\setlength{\tabcolsep}{4pt}
		\begin{tabular}{ccc}
			\toprule
			$\Delta$$C$             &  \comb{}-5  & \comb{}-10 \\ 
			\midrule
			$<0$  & 40.7\% & 33.3\% \\ 
			$=0$  & 25.9\% & 18.5\% \\ 
			$>0$  & 33.3\% & 48.1\% \\

			\bottomrule
		\end{tabular}
		\caption {\jtime{} - Diagnosis Performance for using \comb{}-5 and \comb{}-10 instead of \sfl{}}
		\label{tab:diagnosis}
	\end{table}
	\normalsize

	\begin{table}[h]
		\centering
		\setlength{\tabcolsep}{4pt}
		\begin{tabular}{ccc}
			\toprule
			$\Delta$$C$             &  \comb{}-5  & \comb{}-10 \\ 
			\midrule
			$<0$  & 36.8\% & 28.9\% \\ 
			$=0$  & 26.3\% & 28.6\% \\ 
			$>0$  & 36.8\% & 50.0\% \\

			\bottomrule
		\end{tabular}
		\caption {\mockito{} - Diagnosis Performance for using \comb{}-5 and \comb{}-10 instead of \sfl{}}
		\label{tab:diagnosis}
	\end{table}
	\normalsize

@@
